---
title: "Exploratory_Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploratory_Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates how exploratory functions like `show_in_excel()`, `which_na()` and `which_this()` can be used.

```{r setup}
library(garlic)
```

# Examples

```{r}
df = iris
```

### Show a data frame in MS Excel

```{r}
show_in_excel(df)
```

It can also be used with pipes.

```{r}
library(dplyr)
df %>% 
   show_in_excel()
```

### Which values are missing?

I'm initialising a vector from 1 to 10 with fifth value as missing `NA`.

```{r}
x = c(1:4, NA, 6:10)
```

Using `which_na()`, I can find index of element in the vector which is `NA`.

```{r}
which_na(x)
```

### Which element is this?

It can identify values that satisfy a criteria. It is kind of a wrapper around dplyr's filter().

```{r}
which_this(iris, "Sepal.Length > 7")
```
